Constraining the Interiors of Asteroids Through Close Encounters

### 2022-08-04 paper/main.tex
Pulled cad-speed data, redid vex and period data.
Pushed some remaining files and decided not to include cadence dependence appendix

  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
  \draw (-3, 3) arc (110:93:6);
  \draw (-2, 3.5) node[anchor=center] {$\theta$};
  \draw (-0.5, 2.5) node[anchor=center] {$|\bm \Omega|$};

@@

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & Strong & Weak \\ \hline
    Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
    Excess velocity ($v_\infty$) & - & - \\
    Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
    Period ($P_\omega$, hr) & $>$7.6 & - \\ \hline
    Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\
    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$1.9 & $<$35 \\
    Cadence ($\Delta t$, min) & $<$15 & - \\
    Data gap ($T_\text{gap}$, hr) & - & - \\ 
    \hline
  \end{tabular}
  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty. Perigee and observational uncertainty are the most constraining properties, followed by rotational period, asteroid length, and observational cadence.}
  \label{tab:threshold-summary}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction. The strong uncertainty thresholds (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}). Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
  \label{fig:spin-uncertainty}
\end{figure}

@@

Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds. These values are $\sigma_\rho / \rho = 10^{-3}$ (weak) and $10^{-4}$ (strong), for density distributions extracted via the lumpy model. They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}. Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the encounter properties. Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines. Bands containing 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.

@@

The time between observations of asteroid angular velocity, (cadence, $\Delta t$), may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.  We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.

Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min. We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points. However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.  This increase is generally where the $\sigma(K_{3m})$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.

We expect this threshold value of $\Delta t$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time). 
\jtd{How these time scales affect the $\Delta t$ threshold is discussed in appendix \ref{app:cadence-tests}.}

>>>>

  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
  \draw (-3, 3) arc (110:93:6);
  \draw (-2, 3.5) node[anchor=center] {$\theta$};

@@

\begin{table}
  \centering
  \begin{tabular}{lll} \hline
    Encounter property & Weak & Strong \\ \hline
    Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
    Excess velocity ($v_\infty$) & - & - \\
    Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
    Period ($P_\omega$, hr) & $>$7.6 & - \\ \hline
    Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\
    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$1.9 & $<$35 \\
    Cadence ($\Delta t$, min) & $<$15 & - \\
    Data gap ($T_\text{gap}$, hr) & - & - \\ 
    \hline
  \end{tabular}
  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty. Perigee and observational uncertainty are the most constraining properties, followed by rotational period, asteroid length, and observational cadence.}
  \label{tab:threshold-summary}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction. The weak uncertainty cut-off (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}). The strong cut-off is never exceeded and thus does not appear. Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
  \label{fig:spin-uncertainty}
\end{figure}

@@

Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds. These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model. They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}. Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the encounter properties. Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines. Bands containing 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.

@@

The time between observations of asteroid angular velocity, (cadence, $\Delta t$), may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.  We measure how the moment uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.

Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min. We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points. However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which depends both on the asteroid rotational period $P_\omega$ and the time scales of its orbit.
